% textlint-disable
In the modern desktop environment, windowing systems allow
multiple applications to be used in a single screen space.
The context of a user, i.e., what the user is trying to do and for
what purpose, is diverse and unspecific, changing from user to user and
from time to time.
However, users can construct screen spaces that suit their various contexts
by installing applications and using them in arbitrary combinations.

In the current immersive environment, on the other hand,
basically one application dominates the user's entire field of view.
Therefore, the 3D space in an immersive environment is a single-context space
that is designed for a specific context, such as a meeting or an event,
by a single application.
The purpose of this research is to realize a multi-context immersive environment
that can support everyday work and life where the context continuously changes,
and to investigate in detail the basic infrastructure software necessary
for this new paradigm.
In the course of this research, I have simultaneously developed "Zwin",
a windowing system for XR that can actually be used, and have been spreading it
as an OSS project.
This paper reports the results of basic research to realize "Zwin,"
including the overall design, the rendering protocol,
and the use of existing 2D applications in an immersive environment.
For the overall design, I summarized the advantages and disadvantages of
similar studies and concluded the design of the system required for
the multi-context immersive environment.
For rendering, I proposed a rendering system with high rendering flexibility
and performance, and robustness against poor quality applications,
and showed that it is sufficient for practical use.
As for the use of existing 2D applications, I showed that cooperation
between 3D applications and existing 2D applications, such as drag-and-drop,
is possible by designing the interaction protocols of 3D applications
to be convertible to those of 2D windowing systems.

In the multi-context immersive environment that lies ahead of this research,
applications from various vendors can be launched simultaneously to create
one immersive environment, and each application only needs to provide
specific functions, not the entire space.
Therefore, the diversity of applications and their developers
is expected to increase.
I hope that this research will lead immersive environments to become
a more open and inclusive market.
% textlint-enable
